Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-04 ijar-npb-ms.tex
Fit failure -> functioning probability.

With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown failure probability $p$, which gives rise under repeated experiments to an observed number of failures, $s$.

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-1}
\caption{Plots of the probability that numerical optimisation is required when $N=100$, $m=3$, $\nl=1$ and $\nu=5$ for changing choices of prior, $y$, as a function of the unknown failure probability, $p$.}
\label{fig:need-to-opt-1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-2}
\caption{Plots of the probability that numerical optimisation is required when $y=0.1$, $m=3$, $\nl=1$ and $\nu=5$ for changing amounts of test data, $N$, as a function of the unknown failure probability, $p$.}
\label{fig:need-to-opt-2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-3}
\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of components in the system, $m$, as a function of the unknown failure probability, $p$.}
\label{fig:need-to-opt-3}
\end{figure}

@@

The worst case scenario is that the prior, $y$, is exactly equal to the true unknown probability of failure, $p$.  Regardless of $y$, optimisation is required less frequently with larger test dataset sizes (increasing $N$), but offset by increasing numbers of components of the same type in a system (increasing $m$).  Not shown is that $\nl$ and $\nu$ clearly do not affect the probability that Theorem 2 does not apply, but also the impact on Lemma 3 is negligible.

@@

Clearly the true failure probability, $p$, is unknown.  Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.

>>>>

With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown functioning probability $p$, which gives rise under repeated experiments to an observed number of functioning components, $s$.

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-1}
\caption{Plots of the probability that numerical optimisation is required when $N=100$, $m=3$, $\nl=1$ and $\nu=5$ for changing choices of prior, $y$, as a function of the unknown functioning probability, $p$.}
\label{fig:need-to-opt-1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-2}
\caption{Plots of the probability that numerical optimisation is required when $y=0.1$, $m=3$, $\nl=1$ and $\nu=5$ for changing amounts of test data, $N$, as a function of the unknown functioning probability, $p$.}
\label{fig:need-to-opt-2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{need-to-opt-3}
\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of components in the system, $m$, as a function of the unknown functioning probability, $p$.}
\label{fig:need-to-opt-3}
\end{figure}

@@

The worst case scenario is that the prior, $y$, is exactly equal to the true unknown probability of functioning, $p$.  Regardless of $y$, optimisation is required less frequently with larger test dataset sizes (increasing $N$), but offset by increasing numbers of components of the same type in a system (increasing $m$).  Not shown is that $\nl$ and $\nu$ clearly do not affect the probability that Theorem 2 does not apply, but also the impact on Lemma 3 is negligible.

@@

Clearly the true functioning probability, $p$, is unknown.  Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.
